\thesistitle

### 2019-07-04 sections/research.tex
Improved type 1 clones shortcomings section

Type 1 clones are in most cases implemented as textual equality between code fragments (except for whitespace and comments). Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type. In such cases refactoring opportunities could be invalidated. An example of such a case is displayed in figure \ref{fig:type1}.

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/type1}
  \caption{Example of a type 1 clone.}
  \label{fig:type1}
\end{figure}

In the example in figure \ref{fig:type1}, we see a type 1 clone consisting of two methods. However, these clones might still be very hard to refactor as we cannot see by this example whether they are functionally equal. Both code fragments use different imported types, some of which imported via a wildcard. Because of this, it is hard to verify which of the used types have the same underlying implementation. This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone. When aiming to automatically refactor clones, applying refactorings to clones as shown in figure \ref{fig:type1}, is bound to be error prone and result in a uncompilable project or a difference in functionality.

>>>>

Type 1 clones are by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} implemented as textual equality between code fragments (except for whitespace and comments). Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type. In such cases, refactoring opportunities could be invalidated. This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone. When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error prone and can result in an uncompilable project or a difference in functionality.

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/type1}
  \caption{Example of a type 1 clone that is functionally different.}
  \label{fig:type1}
\end{figure}

In the example in figure \ref{fig:type1}, we see a type 1 clone consisting of two methods. However, these clones might still be very hard to refactor as we cannot see by this example whether they are functionally equal. Both code fragments use different imported types, some of which imported via a wildcard. Because of this, it is hard to verify which of the used types have the same underlying implementation.
